---
title: "Shiny"
subtitle: "Se Statistic"  
author: 
  - "Flo"
  - "Rudi"
  - "Manuel"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
xaringanthemer::style_duo(
  primary_color = "#1F4257",
  secondary_color =  "#F97B64"
)
```
class: inverse, center

#Agenda

--

1.Was ist Shiny

--

2.Frontend/Backend

--

3.Layout  

--

4.Shiny Input/Output  

--

5.Shiny Reactive

--

6.Abschluss

---
class: inverse, center, middle
#1. Was ist Shiny
---
###Was ist Shiny
...
---
class: inverse, center, middle
#2. Frontend/Backend
---
###Frontend/Backend
...
---
class: inverse, center, middle
#3. Layout  
---
### Layout
...
---
class: inverse, center, middle
#4. Shiny Input/Output  
---
###Shiny Input/Output
...
---
class: inverse, center, middle
#5. Shiny Reactive
---
###Shiny Reactive
...
---
class: inverse, center, middle
#6. Abschluss
---
###Abschlus
---
...
---
